A Study on Neural Models for Target-Based Computer-Assisted Musical Orchestration

### 2020-10-06 paper/aimusic2020/paper.tex
Correct table description

\begin{table*}
	\centering    
  \resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}}
    \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \ref{distance} was used to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}\label{orch_eval}
\end{table*}

>>>>

\begin{table*}
	\centering    
  \resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}}
    \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \ref{distance} was used to compute distances between orchestrations and targets. What is shown is the ratio between the distance of Orchidea's solution to the target and our solution's distance to the same target. A value less than 1 means that our model performed worse (i.e. had a larger distance), and a value greater than 1 means our model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}\label{orch_eval}
\end{table*}
